\documentclass[a4paper,10pt]{article}

% === PACKAGE IMPORTS ===
\usepackage[a4paper, margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{url}
\usepackage{fontawesome5}

% === DOCUMENT SETUP ===
\pagestyle{empty}
\setlength{\parindent}{0pt}
\urlstyle{same}

% === CUSTOM COMMANDS ===
\definecolor{heading}{HTML}{2E86C1}
\newcommand{\sect}[1]{\vspace{8pt}\noindent\textbf{\color{heading}\large #1}\vspace{3pt}\hrule\vspace{6pt}}

% === DOCUMENT START ===
\begin{document}

% === HEADER ===
\begin{center}
  {\LARGE \textbf{Viraj Bulugahapitiya}} \\
  18/A, Lytton Road, New Barnet, EN5 5BY \\
  \vspace{3pt}
  \href{mailto:amanthavirajavb@gmail.com}{\faEnvelope\;amanthavirajavb@gmail.com} \quad
  \href{https://linkedin.com/in/viraj97}{\faLinkedin\;linkedin.com/in/viraj97} \quad
  \href{https://github.com/Viraj97-SL}{\faGithub\;github.com/Viraj97-SL} \quad
  \href{https://viraj-bulugahapitiya.vercel.app}{\faGlobe\;viraj-bulugahapitiya.vercel.app}
\end{center}

% === PROFESSIONAL SUMMARY ===
\sect{Professional Summary}
Results-oriented Data Scientist with an MSc in Data Science and proven expertise in end-to-end analytical pipelines, predictive modelling, and research-grade AI. Developed a tri-modal deep learning framework for Alzheimer's detection (AUC-ROC 0.9611), a production XGBoost sports analytics engine processing 565K+ records, and an autonomous multi-agent data curation pipeline with HITL validation. Experienced in statistical modelling, NLP, computer vision, and translating complex, noisy datasets into clear, actionable insights. Skilled in Python, SQL, Power BI, and modern ML frameworks, with a practical background in operations data and supply chain analytics. Active Volunteer Data Scientist with DataKind UK.

% === TECHNICAL SKILLS ===
\sect{Technical Skills}
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]
    \item \textbf{Languages \& Analysis:} Python, SQL, R, Pandas, NumPy, SciPy, Pydantic V2.
    \item \textbf{Machine Learning \& Modelling:} scikit-learn, XGBoost, PyTorch, TensorFlow, Keras, SHAP (Explainability), Ensemble Methods, Genetic Algorithms (DEAP), Statistical Modelling.
    \item \textbf{Deep Learning \& NLP:} 3D Swin Transformers, LSTM, HuggingFace Transformers, SBERT, BM25, RAG, LangChain / LangGraph.
    \item \textbf{Computer Vision:} OpenCV, YOLOv8, ANTsPy, NiBabel, MONAI.
    \item \textbf{Data Visualisation \& BI:} Power BI, Matplotlib, Seaborn, openpyxl.
    \item \textbf{Infrastructure \& Deployment:} PostgreSQL, SQLite, Docker, FastAPI, GCP, Azure, Railway, Git / GitHub Actions.
\end{itemize}

% === WORK EXPERIENCE ===
\sect{Work Experience}

% --- Role 1: Independent ---
\noindent\textbf{Independent Data Scientist \& AI Researcher} \hfill \textit{Oct 2024 -- Present} \\
\textit{Self-Directed | Portfolio \& Open-Source Projects}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Built a production \textbf{predictive analytics platform (CricOracle 2026)}, processing \textbf{565,377 T20 cricket records} to forecast match outcomes with XGBoost (leakage-free \textbf{AUC 0.887}); integrated SHAP TreeExplainer for interpretable predictions and deployed inference via FastAPI.
    \item Designed the \textbf{Matchmaker scoring pipeline} in JobForge AI: a hybrid SBERT cosine similarity + BM25 + Jaccard skill overlap ensemble pre-screen, followed by Gemini Flash \textbf{6-dimensional LLM scoring} across technical skills, domain fit, seniority, visa status, location, and role alignment — processing 200+ job descriptions per run.
    \item Architected \textbf{RepoSentinel}, an autonomous LangGraph DAG that crawls arXiv, YouTube, and Tavily APIs to surface relevant Data Science content, enforcing multi-stage validation (link integrity, syntax, deduplication) and HITL GitHub PR approval before ingestion.
    \item Conducted multimodal sentiment analysis research combining CNN-extracted image features with LSTM text features, demonstrating measurable uplift over unimodal baselines on the IMDB dataset.
    \item \textbf{Volunteer Data Scientist}, DataKind UK (Aug 2025 -- Present); \textbf{Mentor (AI Engineering)}, Teens in AI UK (Feb 2026).
\end{itemize}
\vspace{4pt}

% --- Role 2: MAS Holdings ---
\noindent\textbf{Executive -- Planning (Operations \& Data)} \hfill \textit{May 2022 -- Sep 2024} \\
\textit{MAS Holdings, Sri Lanka}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Drove plant capacity utilisation to \textbf{97\%} and boosted on-time delivery to \textbf{95\%} through proactive data-driven planning, root-cause analysis, and cross-functional coordination.
    \item Built and maintained \textbf{Power BI dashboards} for real-time KPI tracking; delivered weekly executive reports synthesising production, WIP, and supply chain data for senior stakeholders.
    \item Enhanced supply chain resilience through structured inventory analysis, achieving a measurable reduction in work-in-progress (WIP) levels.
\end{itemize}
\vspace{4pt}

% --- Role 3: M&S (condensed) ---
\noindent\textbf{Customer Assistant} \hfill \textit{Feb 2025 -- Present} \\
\textit{Marks and Spencer, London, UK}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Maintained operational accuracy across stock management and digital PoS systems in a high-volume UK retail environment.
\end{itemize}
\vspace{4pt}

% --- Role 4: CICT ---
\noindent\textbf{Trainee -- Planning} \hfill \textit{Dec 2020 -- Jul 2021} \\
\textit{Colombo International Container Terminals (CICT), Sri Lanka}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Monitored key terminal throughput metrics to identify operational bottlenecks; utilised SAP ERP for vessel scheduling, resource allocation, and yard optimisation.
\end{itemize}

% === PROJECTS & RESEARCH ===
\sect{Projects \& Research}

% --- Project 1: Alzheimer's ---
\noindent\textbf{Early Detection of Alzheimer's Disease Using 3D Swin Transformer} \hfill \textit{MSc Research Project}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Developed a novel \textbf{tri-modal deep learning framework} integrating 3D MRI scans, longitudinal clinical data, and biomarker sequences from the ADNI dataset (N=187); pre-trained a \textbf{3D Swin Transformer} with SimCLR-style self-supervised contrastive learning to address data scarcity in a low-sample regime.
    \item Implemented dual \textbf{LSTM networks} for sequential modelling of cognitive assessments and biomarker time-series, fused via a dynamic gated mechanism that adaptively weights each modality per patient.
    \item Achieved \textbf{Accuracy = 89.66\%, AUC-ROC = 0.9611, MCC = 0.8337, G-Mean = 0.9129} on a three-class classification (CN / MCI / Dementia) demonstrating balanced performance under severe class imbalance.
\end{itemize}
\textit{Technologies: Python, PyTorch, ANTsPy, NiBabel, scikit-learn, MONAI, GCP, ADNI Dataset}

\textit{GitHub: \url{https://github.com/Viraj97-SL/Research-Early-prediction-of-Alzheimer-s.git}}
\vspace{8pt}

% --- Project 2: CricOracle ---
\noindent\textbf{CricOracle 2026 -- ML Match \& Score Predictor} \hfill \textit{Production ML Pipeline}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Processed \textbf{565,377 historical T20 cricket records} to forecast ICC World Cup match outcomes and first-innings scores; applied permutation augmentation to eliminate team-ordering bias in the training data.
    \item Trained XGBoost achieving leakage-free \textbf{AUC = 0.887} with Platt Scaling calibration; deployed SHAP TreeExplainer to surface transparent, human-readable key factors per prediction.
    \item Designed a DEAP Genetic Algorithm for automated squad selection under venue and opponent constraints, with full inference served via FastAPI.
\end{itemize}
\textit{Technologies: Python, XGBoost, PyTorch (LSTM), scikit-learn, SHAP, DEAP, FastAPI, Pandas}
\vspace{8pt}

% --- Project 3: Multimodal Sentiment ---
\noindent\textbf{Multimodal Sentiment Analysis on IMDB Reviews} \hfill \textit{Research Project}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Developed a multimodal sentiment model fusing CNN-extracted movie poster features with LSTM-encoded text reviews; conducted a rigorous comparative analysis demonstrating performance uplift of the multimodal architecture over unimodal baselines on the IMDB dataset.
\end{itemize}
\textit{GitHub: \url{https://github.com/Viraj97-SL/IMDB-Multimodal-Analyse-with-Keras}}

% === EDUCATION ===
\sect{Education}
\noindent\textbf{MSc in Data Science} \hfill \textit{Completed, Sep 2025} \\
\textit{University of Hertfordshire, UK}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=0pt]
    \item Modules: Machine Learning, Deep Learning, Neural Networks, Data Visualisation, Data Mining, Applied Data Science, Fundamentals of Data Science.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Diploma in Data Science} \hfill \textit{Apr 2023 -- Apr 2024} \\
\textit{NIBM, Sri Lanka}
\vspace{4pt}

\noindent\textbf{BSc in Logistics Management} \hfill \textit{Oct 2017 -- Oct 2021} \\
\textit{Dalian Maritime University, China}

% === CERTIFICATIONS & AWARDS ===
\sect{Certifications \& Awards}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt, topsep=2pt]
    \item \textbf{Certification:} AI Agents in LangGraph -- LangChain \& Tavily
    \item \textbf{Certification:} Orchestrating Workflows for GenAI Applications -- Astronomer
    \item \textbf{Certification:} Microsoft Certified: Azure AI Fundamentals
    \item \textbf{Award:} Winner, University of Hertfordshire Agentic AI Competition (VisionAID)
\end{itemize}

% === REFERENCES ===
\sect{References}
Available upon request.

\end{document}