\documentclass[a4paper,10pt]{article}

% === PACKAGE IMPORTS ===
\usepackage[a4paper, margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{url}
\usepackage{fontawesome5}

% === DOCUMENT SETUP ===
\pagestyle{empty}
\setlength{\parindent}{0pt}
\urlstyle{same}

% === CUSTOM COMMANDS ===
\definecolor{heading}{HTML}{2E86C1}
\newcommand{\sect}[1]{\vspace{8pt}\noindent\textbf{\color{heading}\large #1}\vspace{3pt}\hrule\vspace{6pt}}

% === DOCUMENT START ===
\begin{document}

% === HEADER ===
\begin{center}
  {\LARGE \textbf{Viraj Bulugahapitiya}} \\
  18/A, Lytton Road, New Barnet, EN5 5BY \\
  \vspace{3pt}
  \href{mailto:amanthavirajavb@gmail.com}{\faEnvelope\;amanthavirajavb@gmail.com} \quad
  \href{https://linkedin.com/in/viraj97}{\faLinkedin\;linkedin.com/in/viraj97} \quad
  \href{https://github.com/Viraj97-SL}{\faGithub\;github.com/Viraj97-SL} \quad
  \href{https://viraj-bulugahapitiya.vercel.app}{\faGlobe\;viraj-bulugahapitiya.vercel.app}
\end{center}

% === PROFESSIONAL SUMMARY ===
\sect{Professional Summary}
Results-oriented Machine Learning Engineer with an MSc in Data Science and hands-on expertise in building, optimising, and deploying end-to-end ML pipelines. Proficient in PyTorch, XGBoost, scikit-learn, and modern MLOps tooling, with a strong foundation in deep learning, predictive modelling, and model explainability (SHAP). Developed research-grade AI solutions including a 3D Swin Transformer for medical imaging (AUC-ROC 0.9611), a production XGBoost sports analytics engine (AUC 0.887), and a live multi-agent pipeline processing 500+ jobs weekly on Railway. Adept at translating complex data into scalable, interpretable machine learning systems deployed via FastAPI, Docker, and cloud infrastructure.

% === TECHNICAL SKILLS ===
\sect{Technical Skills}
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=2pt]
    \item \textbf{Machine \& Deep Learning:} PyTorch, TensorFlow, XGBoost, scikit-learn, Ensemble Methods, Genetic Algorithms (DEAP), SHAP (Model Explainability), 3D Swin Transformers, LSTM, SimCLR Self-Supervised Learning.
    \item \textbf{MLOps \& Data Engineering:} Python, SQL, Pandas, NumPy, Pydantic V2, Docker, Git / GitHub Actions (CI/CD), Structured Logging (structlog).
    \item \textbf{Information Retrieval:} SBERT (sentence-transformers), BM25 (rank-bm25), Jaccard Similarity, ChromaDB / FAISS vector stores.
    \item \textbf{Cloud \& Backend Deployment:} FastAPI, PostgreSQL, SQLite, GCP, Azure, Railway, REST APIs.
    \item \textbf{GenAI \& Computer Vision:} LangGraph, LangChain, Gemini Pro/Flash, OpenCV, YOLOv8, HuggingFace Transformers, RAG.
\end{itemize}

% === WORK EXPERIENCE ===
\sect{Work Experience}

% --- Role 1: Independent ---
\noindent\textbf{Independent ML Engineer \& Researcher} \hfill \textit{Oct 2024 -- Present} \\
\textit{Self-Directed | Portfolio \& Open-Source Projects}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Developed \textbf{CricOracle 2026}, a production ML pipeline processing \textbf{565,377 records} to forecast ICC T20 World Cup match outcomes; trained XGBoost with permutation augmentation to eliminate team-ordering bias, achieving a leakage-free \textbf{AUC of 0.887} calibrated via Platt Scaling, with SHAP TreeExplainer for transparent inference.
    \item Designed a \textbf{Genetic Algorithm (DEAP)} to autonomously optimise 11-player squads based on venue constraints, opponent strength, and sub-continent conditions; inference served via FastAPI.
    \item Architected the \textbf{Matchmaker module} of JobForge AI: an SBERT + BM25 + Jaccard ensemble pre-screen reducing 577 raw scraped jobs to \textasciitilde130 candidates, followed by Gemini Flash 6-dimension LLM scoring (technical skills, domain fit, seniority, visa, location, role alignment), deployed live on Railway.
    \item Built \textbf{RepoSentinel}, an autonomous LangGraph DAG pipeline that crawls arXiv, YouTube, and Tavily APIs to fill content gaps, enforcing multi-stage validation (Markdown, HTTP, Python syntax, deduplication) with a HITL GitHub PR approval mechanism via PyGithub.
    \item \textbf{Mentor (AI Engineering)}, Teens in AI UK (Feb 2026); \textbf{Volunteer Data Scientist}, DataKind UK (Aug 2025 -- Present).
\end{itemize}
\vspace{4pt}

% --- Role 2: MAS Holdings ---
\noindent\textbf{Executive -- Planning (Operations \& Data)} \hfill \textit{May 2022 -- Sep 2024} \\
\textit{MAS Holdings, Sri Lanka}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Drove plant capacity utilisation to \textbf{97\%} and on-time delivery to \textbf{95\%} through data-driven cross-functional planning; reduced WIP inventory through supply chain optimisation.
    \item Built and maintained Power BI dashboards for real-time KPI tracking, translating complex operational data into actionable insights for senior stakeholders.
\end{itemize}
\vspace{4pt}

% --- Role 3: M&S (condensed) ---
\noindent\textbf{Customer Assistant} \hfill \textit{Feb 2025 -- Present} \\
\textit{Marks and Spencer, London, UK}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Maintained operational accuracy across stock management and digital PoS systems in a high-volume UK retail environment.
\end{itemize}
\vspace{4pt}

% --- Role 4: CICT ---
\noindent\textbf{Trainee -- Planning} \hfill \textit{Dec 2020 -- Jul 2021} \\
\textit{Colombo International Container Terminals (CICT), Sri Lanka}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=1pt]
    \item Monitored terminal throughput metrics to identify operational bottlenecks; utilised SAP ERP for vessel scheduling and yard optimisation.
\end{itemize}

% === PROJECTS & RESEARCH ===
\sect{Projects \& Research}

% --- Project 1: CricOracle ---
\noindent\textbf{CricOracle 2026 -- ML Match \& Score Predictor} \hfill \textit{Production ML Pipeline}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Processed \textbf{565,377 records} to forecast match win probabilities and first-innings scores for the ICC T20 World Cup; implemented permutation augmentation to eliminate team-ordering bias from the training set.
    \item Achieved leakage-free \textbf{AUC = 0.887} on an XGBoost classifier, calibrated via Platt Scaling; integrated \textbf{SHAP TreeExplainer} to deliver human-readable key prediction factors alongside each forecast.
    \item Designed a DEAP \textbf{Genetic Algorithm} for autonomous squad optimisation under venue, opponent strength, and pitch condition constraints; full inference pipeline deployed via \textbf{FastAPI}.
\end{itemize}
\textit{Technologies: Python, XGBoost, PyTorch (LSTM), scikit-learn, SHAP, DEAP, FastAPI, Pandas}
\vspace{8pt}

% --- Project 2: Alzheimer's ---
\noindent\textbf{Early Detection of Alzheimer's Disease} \hfill \textit{MSc Research Project}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Developed a tri-modal deep learning framework integrating 3D MRI scans, longitudinal clinical data, and biomarker sequences from the ADNI dataset (N=187); pre-trained a \textbf{3D Swin Transformer} with SimCLR-style self-supervised contrastive learning to address data scarcity.
    \item Implemented dual \textbf{LSTM networks} for temporal sequential modelling, fused via a dynamic gated mechanism that adaptively weights each modality per patient.
    \item Achieved \textbf{Accuracy = 89.66\%, AUC-ROC = 0.9611, MCC = 0.8337, G-Mean = 0.9129} on a three-class classification (CN / MCI / Dementia) under severe class imbalance.
\end{itemize}
\textit{Technologies: Python, PyTorch, ANTsPy, NiBabel, scikit-learn, MONAI, GCP}
\vspace{8pt}

% --- Project 3: RepoSentinel ---
\noindent\textbf{RepoSentinel -- AI/ML Learning Hub Curation Pipeline} \hfill \textit{Autonomous Data Pipeline}
\begin{itemize}[leftmargin=*, topsep=4pt, itemsep=2pt]
    \item Architected a LangGraph DAG pipeline that autonomously crawls Tavily, arXiv, and YouTube APIs to identify and fill content gaps in an open-source Data Science repository.
    \item Engineered a multi-stage validation gate enforcing Markdown formatting, HTTP link validity, Python syntax checks, and deduplication before ingestion.
    \item Integrated a Human-in-the-Loop (HITL) approval mechanism triggering automated GitHub branching and Pull Request creation via PyGithub upon authorisation.
\end{itemize}
\textit{Technologies: Python, LangGraph, PostgreSQL, PyGithub, Docker, REST APIs}

% === EDUCATION ===
\sect{Education}
\noindent\textbf{MSc in Data Science} \hfill \textit{Completed, Sep 2025} \\
\textit{University of Hertfordshire, UK}
\begin{itemize}[leftmargin=*, topsep=2pt, itemsep=0pt]
    \item Modules: Machine Learning, Deep Learning, Neural Networks, Statistical Modelling, Data Mining.
\end{itemize}
\vspace{4pt}

\noindent\textbf{Diploma in Data Science} \hfill \textit{Apr 2023 -- Apr 2024} \\
\textit{NIBM, Sri Lanka}
\vspace{4pt}

\noindent\textbf{BSc in Logistics Management} \hfill \textit{Oct 2017 -- Oct 2021} \\
\textit{Dalian Maritime University, China}

% === CERTIFICATIONS & AWARDS ===
\sect{Certifications \& Awards}
\begin{itemize}[leftmargin=*, itemsep=0pt, parsep=0pt, topsep=2pt]
    \item \textbf{Certification:} AI Agents in LangGraph -- LangChain \& Tavily
    \item \textbf{Certification:} Orchestrating Workflows for GenAI Applications -- Astronomer
    \item \textbf{Certification:} Microsoft Certified: Azure AI Fundamentals
    \item \textbf{Award:} Winner, University of Hertfordshire Agentic AI Competition (VisionAID)
\end{itemize}

% === REFERENCES ===
\sect{References}
Available upon request.

\end{document}